week getbackontrack

### 2024-11-04 1definedata.Rmd
definedataprogressiguess

# require(RSiena)
# require(RsienaTwoStep)

@@

# Jochem messed up and did: waves, rows, columns [1, , ]
socwave1 <- testsoc$nets[ , ,1]  #rows, columns, waves
socwave2 <- testsoc$nets[ , ,2]  #rows, columns, waves
# let us put the diagonal to zero
diag(socwave1) <- 0
diag(socwave2) <- 0
# we want a binary tie (not a weighted tie)
socwave1[socwave1 > 1] <- 1
socwave2[socwave2 > 1] <- 1
# put the nets in an array
net_soc_array <- array(data = c(socwave1, socwave2), dim = c(dim(socwave1), 2))

str(net_soc_array)  #now we basically restructured this 
# output: num [1:50, 1:50, 1:2] 0 0 0 0 0 0 0 0 0 0
```

@@

```{r}
# Jochem messed up and did: waves, rows, columns [1, , ]
polwave1 <- testpolsci$nets[ , ,1]  #rows, columns, waves
polwave2 <- testpolsci$nets[ , ,2]  #rows, columns, waves
# let us put the diagonal to zero
diag(polwave1) <- 0
diag(polwave2) <- 0
# we want a binary tie (not a weighted tie)
polwave1[polwave1 > 1] <- 1
polwave2[polwave2 > 1] <- 1
# put the nets in an array
net_pol_array <- array(data = c(polwave1, polwave2), dim = c(dim(polwave1), 2))

@@

### **QUESTION:**

@@

### QUESTION TO THE ANSWER:

@@

```{r}
# dependent
# net <- sienaDependent(net_soc_array)

# dependent 
nets <- testsoc$nets

@@

@@

```{r}
# dependent:
# net <- sienaDependent(net_soc_array)

>>>>

require(RSiena)
require(RsienaTwoStep)

@@

# Jochem messed up and did: waves, rows, columns [1, , ]
socwave1 <- testsoc$nets[1, , ]  #rows, columns, waves
socwave2 <- testsoc$nets[2, , ]  #rows, columns, waves
# let us put the diagonal to zero
diag(socwave1) <- 0
diag(socwave2) <- 0
# we want a binary tie (not a weighted tie)
socwave1[socwave1 > 1] <- 1
socwave2[socwave2 > 1] <- 1
# put the nets in an array
net_soc_array <- array(data = c(socwave1, socwave2), dim = c(dim(socwave1), 2))

str(net_soc_array)  #now we basically restructured this 
# output: num [1:50, 1:50, 1:2] 0 0 0 0 0 0 0 0 0 0

# dependent
net <- sienaDependent(net_soc_array)
```

HOW COME: when I "correct" Jochem and put [rows,columns,waves] instead of [waves, rows, columns], the sienaDependent function does not work, but it DOES work if I leave the "incorrect" version unchanged?!

@@

```{r}
# Jochem messed up and did: waves, rows, columns [1, , ]
polwave1 <- testpolsci$nets[1, , ]  #rows, columns, waves
polwave2 <- testpolsci$nets[2, , ]  #rows, columns, waves
# let us put the diagonal to zero
diag(polwave1) <- 0
diag(polwave2) <- 0
# we want a binary tie (not a weighted tie)
polwave1[polwave1 > 1] <- 1
polwave2[polwave2 > 1] <- 1
# put the nets in an array
net_pol_array <- array(data = c(polwave1, polwave2), dim = c(dim(polwave1), 2))

@@

### **(old) QUESTION:**

@@

## (new) QUESTION:

@@

```{r}
# # dependent
# net <- sienaDependent(net_soc_array)

# dependent ?
# nets <- testsoc$nets

@@

?full_join

@@

### RSiena troubleshooting

(Cannot install RSiena for some reason.)

```{r}
#require(RSiena)
#require(RsienaTwoStep)
```

Changed administration rights in properties to get around the "file not found"-error.

```{r}
# dependent:
# net <- sienaDependent(net_soc_array) # Does not work "need 2 node sets for a bipartite network"

#also this is only the array for sociology, I need to have a combined DV for both departments for RQ1 ...

# str(net_soc_array)
# my output here: 1:2, 1:50, 1:2
# but in week 5-2: 1:50, 1:50, 1:2

# net <- sienaDependent(net_soc_array) # Which array to take

### 2024-11-04 week5-2.Rmd
definedataprogressiguess

# Packages
```{r}
#install.packages("tidyverse")
require (tidyverse)
require (RSiena)

@@

# didnt' make the IV gender butif i Had: mydata <- sienaDataCreate(net, gender)

>>>>

# Packages
```{r}
#install.packages("tidyverse")
require (tidyverse)
require (RSiena)
#require(RsienaTwoStep

@@

# didnt' make the IV gender butif i Had: 
# mydata <- sienaDataCreate(net, gender)

### 2024-11-04 weekbacktrack.Rmd
definedataprogressiguess

| ![](images/socialnetworking_meh.jpg){width="800"}\                                            | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking.jpg){width="800"}Specify model [S4]           | ![](images/timetopanic.gif){width="800"}[Grandmas bday] |
| & create effects structure [S2]                                                               |                                                            |                                                               | Plotting & revisit RQs                                                                     | Revisit RQs                                                     |                                                                           |                                                         |
|                                                                                               |                                                            |                                                               |                                                                                            |                                                                 | Plotting                                                                  |                                                         |
| Plotting                                                                                      |                                                            |                                                               | Initial description [S3]                                                                   | rewrite intro and Theory [W]                                    |                                                                           |                                                         |

@@

| revisit RQs                                                                                   |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                         |

@@

| ![](images/socialnetworking_meh.jpg){width="800"}                                             | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking.jpg){width="800"}Data & methods part [W]\                      | ![](images/socialnetworking.jpg){width="800"}estimate model     | ![](images/socialnetworking.jpg){width="800"}goodness of fit [S6]         | ![](images/kermit-panic.gif)                            |

@@

| Data & methods part [W]                                                                       |                                                            |                                                               |                                                                                            | Plotting                                                        | Start Results [W]                                                         | [chores at home and university]                         |

@@

|                                                                                               |                                                            |                                                               |                                                                                            | Discussion & conclusion [W]                                     | ![](images/kermit-panic.gif){width="500"}Format project website& hand in! |                                                         |

>>>>

| ![](images/socialnetworking_meh.jpg){width="800"}\                                            | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking_meh.jpg){width="800"}\                                         | ![](images/socialnetworking.jpg){width="800"}\                  | ![](images/socialnetworking.jpg){width="800"}rewrite intro and Theory [W] | ![](images/timetopanic.gif){width="800"}[Grandmas bday] |
| fix package error,                                                                            |                                                            |                                                               | Read Jochems answer & revisit RQs                                                          | Initial description [S3]                                        |                                                                           |                                                         |
|                                                                                               |                                                            |                                                               |                                                                                            |                                                                 | Specify model [S4]                                                        |                                                         |
| Define variables (get stuck with sienaDependent)                                              |                                                            |                                                               | & create effects structure [S2]                                                            | Plotting& Revisit RQs                                           |                                                                           |                                                         |

@@

| check in with Jochem                                                                          |                                                            |                                                               | Plotting & revisit RQs                                                                     |                                                                 |                                                                           |                                                         |
| Plotting                                                                                      |                                                            |                                                               |                                                                                            |                                                                 |                                                                           |                                                         |

@@

| ![](images/socialnetworking_meh.jpg){width="800"}Data & methods part [W]                      | ![](images/used_arson%20frog.jpg){width="952"}[university] | ![](images/used_arson%20frog.jpg)[university]                 | ![](images/socialnetworking.jpg){width="800"}Data & methods part [W]\                      | ![](images/socialnetworking.jpg){width="800"}estimate model     | ![](images/socialnetworking.jpg){width="800"}goodness of fit [S6]         | ![](images/kermit-panic.gif)                            |

@@

| Check in with Jochem                                                                          |                                                            |                                                               |                                                                                            | Plotting                                                        | Start Results [W]                                                         | [chores at home and university]                         |

@@

| Check in with Jochem?                                                                         |                                                            |                                                               |                                                                                            | Discussion & conclusion [W]                                     | ![](images/kermit-panic.gif){width="500"}Format project website& hand in! |                                                         |
